Instrument development

### 2024-05-28 Rmd/Paper1.Rmd
Gjorde om til apa7 ref.: https://bookdown.org/yihui/rmarkdown-cookbook/bibliography.html

---
title: "Instrument development"
author: "Niklas Karlsen, e-post: ..."
date: "2024-05-28"
bibliography: "../data/meta_data/references.bib"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true

@@

TODO

* gjøre om referanser til APA7

@@

The development of a measure usually follows three stages (@boateng_best_2018):

@@

The first stage is described in Paper 1. This computational essay (@odden_using_2023) describes the analysis behind the results in paper 1, and emphasises the quantitative analyses done in the final two stages. This concerns item reduction and extraction of factors (EFA) in stage two, and test of dimensionality (CFA) and tests of reliability and validity in stage three.

@@

When we have as few as five answer alternatives (i.e., 5-pt Likert scale), there are weighty arguments for considering the data as ordinal (Flora et al., 2012; @izquierdo_exploratory_2014; @watkins_exploratory_2018). Five answer alternatives do however begin to imitate an interval scale (i.e., a continous scale). Thus, researchers have also argued for considering 5-pt scales as being continous (Christophersen, 2018; @norman_likert_2010). In order to use the full arsenal of parametric methods (i.e., the properties of the sample are decided by a few parameters), such as maximum likelihood (ML), we decided to consider the data as interval. To support this choice further, we also presented the five alternatives as points on a linear scale in our questionnaire to help the respondents visualise the alternatives as being on an interval scale.

@@

Missing data reduces the size of the dataset used for analysis, which leads to lower power (i.e., larger chances for Type II-error, that is not detecting significant effects, obtaining false negatives). There are different advice for how to handle missing data, depending on whether they are missing at random (MAR), completely at random (MCAR) or not at random (NMAR) (@rubin_inference_1975; @schafer_missing_2002). Data that are missing at random are correlated with the questionnaire (i.e., a question may be missing from a specific version of a questionnaire, which is in a sense random). Data that are missing completely at random, do however not correlate with anything obvious. They are in a sense, seemingly truly random, with no clear rationale for their missing other than circumstance. Data missing not at random are questions that correlate with the question itself (i.e., several respondents may avoid a specific question, i.e., about gender, there seems to be a rationale, that is not a random cause, for data missing for this specific item).

Ways to handle missing data is predictive mean matching when less than 10 % are missing, otherwise ML-methods (@weston_brief_2006; Flora et al., 2012; Watkins, 2018; @mcneish_challenging_2017; @gallagher_introduction_2013).

>>>>

---
title: "Instrument development"
author: "Niklas Karlsen, e-post: ..."
date: "2024-05-28"
bibliography: "../data/meta_data/references.bib"
csl: "../scripts/university-of-gothenburg-apa-7th-edition-swedish-legislations.csl"
output: 
  html_document:
    toc: true
    toc_depth: 3
    toc_float: true

@@

@@

The development of a measure usually follows three stages [@boateng_best_2018]:

@@

The first stage is described in Paper 1. This computational essay [@odden_using_2023] describes the analysis behind the results in paper 1, and emphasises the quantitative analyses done in the final two stages. This concerns item reduction and extraction of factors (EFA) in stage two, and test of dimensionality (CFA) and tests of reliability and validity in stage three.

@@

When we have as few as five answer alternatives (i.e., 5-pt Likert scale), there are weighty arguments for considering the data as ordinal [@flora_old_2012; @izquierdo_exploratory_2014; @watkins_exploratory_2018]. Five answer alternatives do however begin to imitate an interval scale (i.e., a continous scale). Thus, researchers have also argued for considering 5-pt scales as being continous [@christophersen_introduksjon_2018; @norman_likert_2010]. In order to use the full arsenal of parametric methods (i.e., the properties of the sample are decided by a few parameters), such as maximum likelihood (ML), we decided to consider the data as interval. To support this choice further, we also presented the five alternatives as points on a linear scale in our questionnaire to help the respondents visualise the alternatives as being on an interval scale.

@@

Missing data reduces the size of the dataset used for analysis, which leads to lower power (i.e., larger chances for Type II-error, that is not detecting significant effects, obtaining false negatives). There are different advice for how to handle missing data, depending on whether they are missing at random (MAR), completely at random (MCAR) or not at random (NMAR) [@rubin_inference_1975; @schafer_missing_2002]. Data that are missing at random are correlated with the questionnaire (i.e., a question may be missing from a specific version of a questionnaire, which is in a sense random). Data that are missing completely at random, do however not correlate with anything obvious. They are in a sense, seemingly truly random, with no clear rationale for their missing other than circumstance. Data missing not at random are questions that correlate with the question itself (i.e., several respondents may avoid a specific question, i.e., about gender, there seems to be a rationale, that is not a random cause, for data missing for this specific item).

Ways to handle missing data is predictive mean matching when less than 10 % are missing, otherwise ML-methods [@weston_brief_2006; @flora_old_2012; @watkins_exploratory_2018; @mcneish_challenging_2017; @gallagher_introduction_2013].
